---
title: "Comparative Analysis on Tour and PCP"
author: "Denise Bradford"
date: "2/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#devtools::install_github("ropenscilabs/ochRe")
#remotes::install_github("casperhart/detourr")
library(tourr)
library(spinifex)
library(geozoo)
library(palmerpenguins)
library(ggpcp)
library(tidyverse)
library(ochRe)
library(gifski)
library(ggplotlyExtra)
library(detourr)
library(viridis)

penguins <- penguins %>% filter(!is.na(bill_length_mm))

```

## Using the Parallel Coordinate Plots (PCP) by Hieke Hofmann

The package ggpcp version versus the ggparallel package gives the user the ability to look at variables that are categorical. 

\begin{itemize}
\item{Pros}
  \begin{itemize}
  \item{High Dimensional Data Visualization}
  \item{Linear Dependences are easy to perceive trends}
  \item{Axes order can be changed to check out trends between two axes}
  \end{itemize}
\item{Cons}
  \begin{itemize}
  \item{Overlaying of data lines for common data values}
  \item{Level of clutter present in the visualization}
  \end{itemize}
\end{itemize}


```{r ggpcp}
penguins %>%
  pcp_select(species, 2:7, species) %>%
  pcp_scale(method="uniminmax") %>%
  pcp_arrange() %>%
  ggplot(aes_pcp()) + 
    geom_pcp_axes() + 
    geom_pcp(aes(colour = species)) + 
    geom_pcp_boxes(stat = "identity", boxwidth = 0.75, color = 'red') +
    scale_color_viridis(discrete = TRUE) + theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=0.5))

```

## Using Tourr by Di Cook 
\begin{itemize}
\item{}
\item{}
\end{itemize}
```{r tourr}
ggplot(penguins, 
   aes(x=flipper_length_mm, 
       y=body_mass_g,
       colour=species,
       shape=species)) +
  geom_point(alpha=0.7, 
             size=2) +
  scale_colour_ochre(
    palette="nolan_ned") + 
  theme(aspect.ratio=1,
  legend.position="bottom")


ggplot(penguins, 
   aes(x=bill_length_mm, 
       y=body_mass_g,
       colour=species,
       shape=species)) +
  geom_point(alpha=0.7, 
             size=2) +
  scale_colour_ochre(
    palette="nolan_ned") + 
  theme(aspect.ratio=1,
  legend.position="bottom")

#Can't be ran in the knit as is, but will run in an html format
clrs <- ochre_pal(
  palette="nolan_ned")(3)
col <- clrs[
  as.numeric(
    penguins$species)]
animate_xy(penguins[,3:6], 
           col=col, 
           axes="off", 
           fps=15)
```

## Using Detourr Package

```{r detourr}

pcs <- penguins %>%
  select(-species, -island,-sex) %>%
  prcomp()

pcs <- as_tibble(pcs$x) %>%
  select(PC1:PC5)

plot_data <- penguins %>%
  select(-(bill_length_mm:body_mass_g), -year) %>%
  bind_cols(pcs)


set.seed(1)

animate_tour(
  plot_data,
  cols = starts_with("PC"),
  grand_tour(2),
  display_scatter(tour_aes(
    colour = species,
    label = c(species, sex, island)
  ),
  axes = FALSE,
  size = 0.5,
  alpha = 0.7
  )
)

```

